2040 greenhouse gas reduction targets

### 2023-06-15 paperCharts.Rmd
additional paper data and charts improvements

@@

Generation <- data.frame(
  Electricity_Generation=c("coal_in_generation_(%)","gas_in_generation_(%)","wind_and_Solar_gen_(%)","wind_and_Solar_cap_(TW)"),
  reference_value=c(
    round(coal_in_generation %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
    round(gas_in_generation %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
    round(wind_and_Solar_gen %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
    round(wind_and_Solar_cap %>% filter(scenario == mainScen) %>% pull(value)/ 1000,1)

    ),
  min = c(
   round(min(coal_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(min(gas_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(min(wind_and_Solar_gen %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(min(wind_and_Solar_cap %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(value)/ 1000),1)
   ),
  max = c(
   round(max(coal_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(max(gas_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(max(wind_and_Solar_gen %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(max(wind_and_Solar_cap %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(value)/ 1000),1)
   )
)

@@

@@

@@

@@

plotData <- rbind(
  df %>% 
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>% 
    mutate(reduction = round(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference) ,2)) %>% 
    select(-variable)
  ,
  df %>% 
    filter(region == "EU27", period %in% c(2035:2050), tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>% 
    mutate(reduction = round(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference) ,2)) %>% 
    select(-variable)
  ) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(x=ifelse(reduction>0,period+1,NA),
         xend=ifelse(reduction>0,period+1,NA),
         y=ifelse(reduction>0,1,NA),
         yend=ifelse(reduction>0,ifelse(reduction<=0,0,reduction),NA),
         bar = ifelse(period==2040,"2040","emi"),
         #label = ifelse(value>0,paste0( "- ", (1-value) * 100, "% (-", (1-intraEURed) * 100 ,"%)"),NA),
         labelY = reduction + (1-reduction)/2,
         labelX=period+1) %>%
  group_by(model,region,period) %>% 
  mutate(max=max(reduction),
         min=min(reduction),
         range=max-min,
         label= paste0(round((1-max) * 100), "% to ", round((1-min) * 100) ,"%"))

@@

g[["Electricity Generation"]] <- 
  ggplot(plotData,aes(x=period,y=percentage)) +
  geom_area(aes(fill=variable),alpha=0.4) +
  geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") +
  geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) +
  #ggrepel::geom_text_repel(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2043.5), vjust=0.5, hjust=0.5, na.rm=TRUE, color = "black", size = 12) +
  #geom_text(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(inv_vars[variable], " (",round(percentage,2)*100,"%)"), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size = 12) +
  geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geom.text.double.size) +
  theme_doubleColumn()  +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks=c(2020,2040,2060)) +
  scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
  theme(axis.title.y=element_blank()) +
  guides(fill=guide_legend(nrow=8,override.aes = list(alpha=1), byrow = TRUE)) +
  #annotate(geom = "text", x = 2022, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage + 0.06, label = "renewables", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) +
  #annotate(geom = "text", x = 2023, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage - 0.06, label = "and nuclear", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) +
  annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) +
  theme(axis.text.y=element_blank()) +
  theme(legend.key.height = unit(0.8, "cm"),
    legend.key.width = unit(0.8,"cm")) +
  theme(legend.spacing.y = unit(0.1, 'cm'))

@@

g[["Solar Photovoltaics capacity"]] <- ggplot(plotData,aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_segment(aes(x=2040, y=0, xend=2040, yend=plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value)), linetype="dashed", color="black") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min), alpha = 0.5, fill = "#545454") + 
    geom_line(data=plotData %>% filter(scenario == mainScen),linewidth=1.5) +
    geom_line(data=h,linewidth=1,linetype="dashed") +
    geom_point(data=plotData %>% filter(scenario == mainScen, period %in% c(2030,2040)),size=3,shape=21,fill="white",stroke=1.5) +
    geom_point(data=target, size=3, shape=4, stroke = 1.5) +
    geom_label_repel(data=target, aes(label = paste0(round(value),"GW - ", target)),box.padding = 0.1,
                  #segment.curvature = -0.1,
                  segment.square = TRUE,
                  point.padding = 0.6,
                  nudge_x = 5,
                  #nudge_y = -0.02,
                  #force = 0.5,
                  hjust = 0,
                  direction="y", size = geom.text.double.size*0.9, xlim = c(2020, 2070)) +
  geom_label_repel(data=plotData %>% filter(scenario == mainScen, period == 2030), aes(label = paste0(round(value),"GW")),box.padding = 0.1,
                  point.padding = 1,
                  nudge_x = -2,
                  nudge_y = 500,
                  hjust = 1, direction="y",
                  size = geom.text.double.size) +
  geom_label_repel(data=plotData %>% filter(scenario == mainScen, period == 2040), aes(label = paste0(round(value),"GW")),box.padding = 0.1,
                  point.padding = 1,
                  nudge_x = -2,
                  nudge_y =500,
                  #hjust = 0, 
                  direction="y",
                  size = geom.text.double.size) +
    theme_doubleColumn() + 
    theme(axis.title.y = element_blank())+
    coord_cartesian(clip = 'off')

@@

g[["Electricity Share"]] <- ggplot(plotData,aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_segment(aes(x=2040, y=0, xend=2040, yend=max(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))), linetype="dashed", color="black") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min, fill=variable), alpha = 0.3) + 
    geom_line(data=plotData %>% filter(scenario == mainScen), linewidth=1.5,aes(color=variable)) +
    #geom_line(data=h,linewidth=1,linetype="dashed") +
    geom_point(data=plotData %>% filter(scenario == mainScen, period == 2040),size=3,shape=21,fill="white",stroke=1.5) +
    geom_line(data=h %>% filter(period >= 2005),linetype="dashed", linewidth = 1, aes(color=variable)) +
    geom_label_repel(data= plotData %>% filter(scenario == mainScen, period == 2040),
                         aes(
                           label = paste0(round(value*100),"%")),
                      box.padding = 3,
                      #segment.curvature = -0.1,
                      segment.square = TRUE,
                      point.padding = 0.6,
                      nudge_x = 5,
                      nudge_y = c(0.55,0.27,-0.05,-0.6),
                      #force = 0.5,
                      #hjust = 0,
                      direction="y"
                      , size = geom.text.double.size*0.9
                      #, xlim = c(2020, 2070)
                      ) +
    scale_colour_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    scale_fill_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    theme_doubleColumn() + 
    scale_y_continuous(labels = scales::percent) +
    expand_limits(y=c(0,1)) +
    guides(color=guide_legend(nrow=2)) +
  theme(axis.title.y = element_blank())

@@

g[["Primary Energy"]] <- ggplot(plotData,aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_segment(aes(x=2040, y=0, xend=2040, yend=max(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))), linetype="dashed", color="black") +
    geom_line(data=plotData %>% filter(scenario == mainScen), aes(color=variable), linewidth=1.5) +
    geom_line(data=h,aes(color=variable),linewidth=1,linetype="dashed") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min, fill=variable), alpha = 0.3) + 
    #geom_point(data=plotData[plotData$period %in% c(2020,2030,2040),],size=4,shape=21,fill="white") +
    geom_point(data=plotData %>% filter(scenario == mainScen, period == 2040),aes(color=variable),size=3,shape=21,fill="white",stroke=1.5) +
    #annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) +
    scale_color_manual(values = c(setNames(options$aesthetics$legend$color[names(vars)],vars)), labels = setNames(names(vars), vars)) +
    scale_fill_manual(values = c(setNames(options$aesthetics$legend$color[names(vars)],vars)), labels = setNames(names(vars), vars)) +
    theme_doubleColumn() + 
    expand_limits(y=c(0,1)) +
    guides(color=guide_legend(nrow=2)) +
    theme(axis.title.y = element_blank()) #+
    #guides(fill = FALSE)

@@

plotData <- df %>% 
  filter(region == "EU27", period  %in% c(2020,2030,2040,2050,2060), scenario == mainScen, variable %in% unlist(vars))

@@

plotDataTotal <- plotData %>%
  group_by(model,scenario,region,unit,period,carrier) %>%
  summarize(value=sum(value),.groups = "keep") %>%
  mutate(type="Total")

>>>>

bdgt <- remindEmi %>% 
  filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen) %>%
    mutate(weight = ifelse(period %in% c(2020,2050),2.5,5),
           budget = value*weight) %>%
    group_by(model,scenario,region,variable,tgt2050,tgt2030,efficiency,bioLim,limCCS) %>%
    summarize(budget=round(sum(budget)/1000,2),.groups = "keep")

budget <- data.frame(
  Budget=c("Emissions with LULUCF and with international transport","Emissions without LULUCF and with international transport","Emissions with LULUCF and with intra-EU aviation","Emissions without LULUCF and with intra-EU aviation"),
  reference_value=c(round(bdgt %>% filter(variable == "Emissions with LULUCF and with international transport", scenario == mainScen) %>% pull(budget)),
                    round(bdgt %>% filter(variable == "Emissions without LULUCF and with international transport", scenario == mainScen) %>% pull(budget)),
                    round(bdgt %>% filter(variable == "Emissions with LULUCF and with intra-EU aviation", scenario == mainScen) %>% pull(budget)),
                    round(bdgt %>% filter(variable == "Emissions without LULUCF and with intra-EU aviation", scenario == mainScen) %>% pull(budget))),
  min = c(round(min(bdgt %>% filter(variable == "Emissions with LULUCF and with international transport") %>% pull(budget))),
                    round(min(bdgt %>% filter(variable == "Emissions without LULUCF and with international transport") %>% pull(budget))),
                    round(min(bdgt %>% filter(variable == "Emissions with LULUCF and with intra-EU aviation") %>% pull(budget))),
                    round(min(bdgt %>% filter(variable == "Emissions without LULUCF and with intra-EU aviation") %>% pull(budget)))),
  max = c(round(max(bdgt %>% filter(variable == "Emissions with LULUCF and with international transport") %>% pull(budget))),
                    round(max(bdgt %>% filter(variable == "Emissions without LULUCF and with international transport") %>% pull(budget))),
                    round(max(bdgt %>% filter(variable == "Emissions with LULUCF and with intra-EU aviation") %>% pull(budget))),
                    round(max(bdgt %>% filter(variable == "Emissions without LULUCF and with intra-EU aviation") %>% pull(budget))))
)

budget %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

nuclear_in_generation <- left_join(
  df %>%
  filter(region == "EU27", period == 2040, variable %in% c("SE|Electricity|Nuclear")) %>%  
  select(scenario,tgt2030,value)
  ,
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% c("SE|Electricity")) %>%
  mutate(total = value) %>%  
  select(scenario,tgt2030,total)
  , by = join_by(scenario == scenario, tgt2030 == tgt2030)
  ) %>%
  mutate(percentage = value/total)

Generation <- data.frame(
  Electricity_Generation=c("coal_in_generation_(%)","gas_in_generation_(%)","nuclear_in_generation_(%)","wind_and_Solar_gen_(%)","wind_and_Solar_cap_(TW)"),
  reference_value=c(
    round(coal_in_generation %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
    round(gas_in_generation %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
    round(nuclear_in_generation %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
    round(wind_and_Solar_gen %>% filter(scenario == mainScen) %>% pull(percentage)*100,1),
    round(wind_and_Solar_cap %>% filter(scenario == mainScen) %>% pull(value)/ 1000,1)

    ),
  min = c(
   round(min(coal_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(min(gas_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(min(nuclear_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(min(wind_and_Solar_gen %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(min(wind_and_Solar_cap %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(value)/ 1000),1)
   ),
  max = c(
   round(max(coal_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(max(gas_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(max(nuclear_in_generation %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(max(wind_and_Solar_gen %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(percentage)*100),1),
   round(max(wind_and_Solar_cap %>% filter(tgt2030 %in% tgt2030Scen) %>% pull(value)/ 1000),1)
   )
)

share_of_fossil_in_electricity <- data.frame(
  FE=c("share_of_fossil_without_CCS_in_electricity_(%)"),
  reference_value_2020=c(
    round((1-df %>% filter(region == "EU27", period == 2020, variable == "SE|Electricity|carbon-free", tgt2030 %in% tgt2030Scen, scenario == mainScen) %>% pull(value))*100 )),
  reference_value_2040=c(
    round((1-df %>% filter(region == "EU27", period == 2040, variable == "SE|Electricity|carbon-free", tgt2030 %in% tgt2030Scen, scenario == mainScen) %>% pull(value))*100 )),
  min = c(round(min((1-df %>% filter(region == "EU27", period == 2040, variable == "SE|Electricity|carbon-free", tgt2030 %in% tgt2030Scen) %>% pull(value))*100))),
  max = c(round(max((1-df %>% filter(region == "EU27", period == 2040, variable == "SE|Electricity|carbon-free", tgt2030 %in% tgt2030Scen) %>% pull(value))*100)))
)

@@

build_UE_heat <- c(
  "Heat pump" = "UE|Buildings|Heating|Electricity|Heat pump",
  "District Heating" = "UE|Buildings|Heating|District Heating",
  "Resistance" = "UE|Buildings|Heating|Electricity|Resistance",
  "Hydrogen" = "UE|Buildings|Heating|Hydrogen",
  "Gases" = "UE|Buildings|Heating|Gases",
  "Liquids" = "UE|Buildings|Heating|Liquids",
  "Solids" = "UE|Buildings|Heating|Solids"#,
#  "non-Heating Electricity" = "UE|Buildings|non-Heating|Electricity|Conventional"
)

build_UE_heating_data <- left_join(
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% build_UE_heat[c("Heat pump","District Heating","Resistance")], tgt2030 %in% tgt2030Scen) %>%
  group_by(scenario) %>%    
  summarize(value = sum(value),.groups = "keep")
  ,
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% build_UE_heat, tgt2030 %in% tgt2030Scen) %>%
  group_by(scenario) %>%  
  summarize(total = sum(value)) %>% 
  select(scenario,total)  
  ,
  by = join_by(scenario == scenario)
) %>% 
  mutate(pctg = value/total)

build_UE_liq_gas_data <- left_join(
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% build_UE_heat[c("Gases","Hydrogen","Liquids")], tgt2030 %in% tgt2030Scen) %>%
  group_by(scenario) %>%    
  summarize(value = sum(value),.groups = "keep")
  ,
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% build_UE_heat, tgt2030 %in% tgt2030Scen) %>%
  group_by(scenario) %>%  
  summarize(total = sum(value)) %>% 
  select(scenario,total)  
  ,
  by = join_by(scenario == scenario)
) %>% 
  mutate(pctg = value/total)

build_UE_solids_data <- left_join(
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% build_UE_heat[c("Solids")], tgt2030 %in% tgt2030Scen) %>%
  group_by(scenario) %>%    
  summarize(value = sum(value),.groups = "keep")
  ,
  df %>% 
  filter(region == "EU27", period == 2040, variable %in% build_UE_heat, tgt2030 %in% tgt2030Scen) %>%
  group_by(scenario) %>%  
  summarize(total = sum(value)) %>% 
  select(scenario,total)  
  ,
  by = join_by(scenario == scenario)
) %>% 
  mutate(pctg = value/total)

share_of_build_UE_heating <- data.frame(
  FE=c("share_of_electric_and_district_buildings_heating_useful energy_(%)","share_of_liquids_and_gases_buildings_heating_useful_energy_(%)","share_of_solids_buildings_heating_useful energy_(%)"),
  reference_value=c(round(build_UE_heating_data %>% filter(scenario == mainScen) %>% summarize(total = sum(pctg),.groups = "keep") %>% pull(total)*100 ),
                    round(build_UE_liq_gas_data %>% filter(scenario == mainScen) %>% summarize(total = sum(pctg),.groups = "keep") %>% pull(total)*100 ),
                    round(build_UE_solids_data %>% filter(scenario == mainScen) %>% summarize(total = sum(pctg),.groups = "keep") %>% pull(total)*100 )),
  min = c(round(min(build_UE_heating_data %>% pull(pctg) *100)),
          round(min(build_UE_liq_gas_data %>% pull(pctg) *100)),
          round(min(build_UE_solids_data %>% pull(pctg) *100))),
  max = c(round(max(build_UE_heating_data %>% pull(pctg) *100)),
          round(max(build_UE_liq_gas_data %>% pull(pctg) *100)),
          round(max(build_UE_solids_data %>% pull(pctg) *100)))
)

build_FE_data <- left_join(
  df %>% 
  filter(region == "EU27", period == 2040, variable == "FE|Buildings|Heating", tgt2030 %in% tgt2030Scen) %>% 
  select(scenario,value)  
  ,
  df %>% 
  filter(region == "EU27", period == 2020, variable == "FE|Buildings|Heating", tgt2030 %in% tgt2030Scen) %>%
  mutate(base = value) %>% 
  select(scenario,base)  
  ,
  by = join_by(scenario == scenario)
) %>% 
  mutate(pctg = value/base)

share_of_build_FE_in_relation_to_2020 <- data.frame(
  FE=c("share_of_build_FE_in_relation_to_2020_(%)"),
  reference_value=c(round((1-build_FE_data %>% filter(scenario == mainScen) %>% pull(pctg))*100 )),
  min = c(round(min((1-build_FE_data %>% pull(pctg)) *100))),
  max = c(round(max((1-build_FE_data %>% pull(pctg)) *100)))
)

@@

share_of_fossil_in_electricity %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

share_of_build_UE_heating %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

share_of_build_FE_in_relation_to_2020 %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

plotData <- rbind(
  df %>% 
    filter(region == "EU27", period %in% c(2030:2040), tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>% 
    mutate(reduction = round(value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference) ,2)) %>% 
    select(-variable)
  ,
  df %>% 
    filter(region == "EU27", period %in% c(2045:2050), tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>% 
    mutate(reduction = round(value / tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference) ,2)) %>% 
    select(-variable)
  ) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(x=ifelse(reduction>0,period+1,NA),
         xend=ifelse(reduction>0,period+1,NA),
         y=ifelse(reduction>0,1,NA),
         yend=ifelse(reduction>0,ifelse(reduction<=0,0,reduction),NA),
         bar = ifelse(period==2040,"2040","emi"),
         #label = ifelse(value>0,paste0( "- ", (1-value) * 100, "% (-", (1-intraEURed) * 100 ,"%)"),NA),
         labelY = reduction + (1-reduction)/2,
         labelX=period+1) %>%
  group_by(model,region,period) %>% 
  mutate(max=max(reduction),
         min=min(reduction),
         range=max-min,
         label= paste0(round((1-max) * 100), "% to ", round((1-min) * 100) ,"%"))

@@

g[["Electricity Generation"]] <- 
  ggplot(plotData,aes(x=period,y=percentage)) +
  geom_area(aes(fill=variable),alpha=0.4) +
  geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") +
  geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) +
  #ggrepel::geom_text_repel(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2043.5), vjust=0.5, hjust=0.5, na.rm=TRUE, color = "black", size = 12) +
  #geom_text(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(inv_vars[variable], " (",round(percentage,2)*100,"%)"), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size = 12) +
  geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geom.text.double.size) +
  theme_doubleColumn()  +
  scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) +
  scale_x_continuous(breaks=c(2020,2040,2060)) +
  scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) +
  theme(axis.title.y=element_blank()) +
  guides(fill=guide_legend(nrow=8,override.aes = list(alpha=1), byrow = TRUE)) +
  #annotate(geom = "text", x = 2022, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage + 0.06, label = "renewables", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) +
  #annotate(geom = "text", x = 2023, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage - 0.06, label = "and nuclear", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) +
  annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) +
  #theme(axis.text.y=element_blank()) +
  theme(legend.key.height = unit(0.8, "cm"),
    legend.key.width = unit(0.8,"cm")) +
  theme(legend.spacing.y = unit(0.1, 'cm')) +
  theme(legend.margin=margin(l = -2, unit='cm'))

@@

g[["Solar Photovoltaics capacity"]] <- ggplot(plotData,aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_segment(aes(x=2040, y=0, xend=2040, yend=plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value)), linetype="dashed", color="black") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min), alpha = 0.5, fill = "#545454") + 
    geom_line(data=plotData %>% filter(scenario == mainScen),linewidth=1.5) +
    geom_line(data=h,linewidth=1,linetype="dashed") +
    geom_point(data=plotData %>% filter(scenario == mainScen, period %in% c(2030,2040)),size=3,shape=21,fill="white",stroke=1.5) +
    geom_point(data=target, size=3, shape=4, stroke = 1.5) +
    geom_label_repel(data=target, aes(label = paste0(round(value),"GW - ", target)),box.padding = 0.1,
                  #segment.curvature = -0.1,
                  segment.square = TRUE,
                  point.padding = 0.6,
                  nudge_x = 5,
                  #nudge_y = -0.02,
                  #force = 0.5,
                  hjust = 0,
                  direction="y", size = geom.text.double.size*0.9, xlim = c(2020, 2070)) +
  geom_label_repel(data=plotData %>% filter(scenario == mainScen, period == 2030), aes(label = paste0(round(value),"GW")),box.padding = 0.1,
                  point.padding = 1,
                  nudge_x = -2,
                  nudge_y = 500,
                  hjust = 1, direction="y",
                  size = geom.text.double.size) +
  geom_label_repel(data=plotData %>% filter(scenario == mainScen, period == 2040), aes(label = paste0(round(value),"GW")),box.padding = 0.1,
                  point.padding = 1,
                  nudge_x = -2,
                  nudge_y =500,
                  #hjust = 0, 
                  direction="y",
                  size = geom.text.double.size) +
    theme_doubleColumn() + 
    theme(axis.title.y = element_blank())+
    coord_cartesian(clip = 'off') +
    expand_limits(y = 3000)

@@

g[["Electricity Share"]] <- ggplot(plotData,aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_segment(aes(x=2040, y=0, xend=2040, yend=max(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))), linetype="dashed", color="black") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min, fill=variable), alpha = 0.3) + 
    geom_line(data=plotData %>% filter(scenario == mainScen), linewidth=1.5,aes(color=variable)) +
    #geom_line(data=h,linewidth=1,linetype="dashed") +
    geom_point(data=plotData %>% filter(scenario == mainScen, period == 2040),size=3,shape=21,fill="white",stroke=1.5) +
    geom_line(data=h %>% filter(period >= 2005),linetype="dashed", linewidth = 1, aes(color=variable)) +
    geom_label_repel(data= plotData %>% filter(scenario == mainScen, period == 2040),
                         aes(
                           label = paste0(round(value*100),"%")),
                      box.padding = 3,
                      #segment.curvature = -0.1,
                      segment.square = TRUE,
                      point.padding = 0.6,
                      nudge_x = 5,
                      nudge_y = c(0.55,0.27,-0.05,-0.6),
                      #force = 0.5,
                      #hjust = 0,
                      direction="y"
                      , size = geom.text.double.size*0.9
                      #, xlim = c(2020, 2070)
                      ) +
    scale_colour_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    scale_fill_manual(values = c("Final Energy|Electricity Share"="black","Final Energy|Transport|Electricity Share"="#a1dd70","Final Energy|Industry|Electricity Share"="#5f6769","Final Energy|Buildings|Electricity Share"="#5edfff"), labels = setNames(names(vars), vars)) +
    theme_doubleColumn() + 
    scale_y_continuous(breaks = seq(0, 1, 0.2),labels = scales::percent) +
    expand_limits(y=c(0,1)) +
    guides(color=guide_legend(nrow=2)) +
  theme(axis.title.y = element_blank())

@@

g[["Primary Energy"]] <- ggplot(plotData,aes(x=period,y=value)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_segment(aes(x=2040, y=0, xend=2040, yend=max(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value))), linetype="dashed", color="black") +
    geom_line(data=plotData %>% filter(scenario == mainScen), aes(color=variable), linewidth=1.5) +
    geom_line(data=h,aes(color=variable),linewidth=1,linetype="dashed") +
    geom_ribbon(aes(ymax = ribbon.max, ymin = ribbon.min, fill=variable), alpha = 0.3) + 
    #geom_point(data=plotData[plotData$period %in% c(2020,2030,2040),],size=4,shape=21,fill="white") +
    geom_point(data=plotData %>% filter(scenario == mainScen, period == 2040),aes(color=variable),size=3,shape=21,fill="white",stroke=1.5) +
    #annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) +
    scale_color_manual(values = c(setNames(options$aesthetics$legend$color[names(vars)],vars)), labels = setNames(names(vars), vars)) +
    scale_fill_manual(values = c(setNames(options$aesthetics$legend$color[names(vars)],vars)), labels = setNames(names(vars), vars)) +
    theme_doubleColumn() + 
    expand_limits(y=c(0,1)) +
    guides(color=guide_legend(nrow=2)) +
    theme(axis.title.y = element_blank()) +
    expand_limits(y = 30)
    #guides(fill = FALSE)

@@

plotData <- df %>% 
  filter(region == "EU27", period  %in% c(2020,2030,2040,2050), scenario == mainScen, variable %in% unlist(vars))

@@

plotDataTotal <- plotData %>%
  group_by(model,scenario,region,unit,period,carrier) %>%
  summarize(value=sum(value),.groups = "keep") %>%
  mutate(type="EU-27 Net-trade")
